Different rules for binocular combination of luminance flicker in cortical and subcortical pathways

### 2023-02-03 manuscriptPLOSBIO.Rmd
Started formatting for PLOS Biology

---
title: "Different rules for binocular combination of luminance flicker in cortical and subcortical pathways"
author: "Federico G. Segala, Aurelio Bruno, Myat T. Aung, Alex R. Wade &  Daniel H. Baker"
date: "Department of Psychology, University of York, UK"
output:
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
    keep_tex: yes
  pdf_document:
    toc: no
  word_document: default
  html_document: default
bibliography: references.bib
csl: pnas.csl
---

@@

**Keywords:** Pupillary light reflex; Pupillometry; EEG; Pupil diameter; Binocular vision; Binocular interactions; Contrast matching; Computational modelling; Psychophysics

**This PDF includes**:

  Main Text (Abstract, Significance Statement, Introduction, Methods, Results, Discussion, Conclusions, Acknowledgments)

  Figures 1 to 6

  Table 1

>>>>

---
title: "Different rules for binocular combination of luminance flicker in cortical and subcortical pathways"
short title: "Binocular combination of flickering light"
author: "Federico G. Segala, Aurelio Bruno, Myat T. Aung, Alex R. Wade &  Daniel H. Baker"
date: "Department of Psychology, University of York, UK"
header-includes: \usepackage{setspace}\doublespacing
output:
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
    keep_tex: yes
  pdf_document:
    toc: no
  word_document: default
  html_document: default
bibliography: references.bib
csl: plos-biology.csl
---

@@

**Keywords:** Pupillary light reflex; Pupillometry; EEG; Pupil diameter; Binocular vision; Binocular interactions; Contrast matching; Computational modelling; Psychophysics
\newpage
